### 2021-10-11 paper/output/document/paper32.tex
feedback

Once again, the notion of permissibility will be useful here.%

@@

  Empty assignment\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This completes my implementation of Kroy's formalization of the first formulation of the 
categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
that it is both non-trivial and consistent. Now it's time to start testing!%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Application Tests\label{sec:app_tests_kroy}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In the following sections, I will use the application and metaethical tests presenting in Sections \ref{sec:app_tests_naive} and \ref{sec:meta_tests_naive}
        to tease out the strengths and weaknesses of Kroy's formalization. While the formalization is considerably
        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means. 
        I will analyze these problems in the context of philosophical scholarship explicating the content 
        of the formula of universal law. The findings in these sections will inform milestones for my
        custom formalization of the categorical imperative. They also serve as an example of how formalized
        and automated ethics can reveal philosophical strengths and weaknesses of an ethical theory.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\textbf{Murder}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
it is actually wrong.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Let the constant $M$ denote murder.%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
at all worlds.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
to imply prohibition at $\text{every world}$.

@@

possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation,
since it holds in the base logic itself.%

@@

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True, $i_2$  := False)
    B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
    w = $i_2$ \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
        DDL itself allows implied contradictions and, as I explored in Section \ref{sec:naive_tests_kroy}, Kroy's 
        formalization doesn't do anything to remedy this.

@@

@@

%:%108=52%:%
%:%109=53%:%

@@

%:%111=54%:%
%:%112=55%:%
%:%113=58%:%
%:%116=61%:%
%:%117=62%:%

@@

%:%123=67%:%
%:%126=69%:%
%:%127=70%:%

@@

@@

%:%134=76%:%
%:%135=77%:%

@@

%:%138=79%:%
%:%140=79%:%
%:%144=79%:%
%:%145=79%:%
%:%147=80%:%
%:%148=81%:%

@@

%:%160=85%:%
%:%161=86%:%

@@

@@

%:%172=96%:%
%:%173=97%:%

@@

%:%176=99%:%
%:%178=99%:%
%:%182=99%:%
%:%183=99%:%
%:%185=100%:%
%:%186=101%:%

@@

%:%198=106%:%
%:%199=107%:%

@@

%:%208=117%:%
%:%209=117%:%
%:%210=118%:%

@@

%:%213=120%:%
%:%215=120%:%
%:%219=120%:%
%:%220=120%:%
%:%222=121%:%
%:%223=122%:%

@@

%:%235=126%:%
%:%236=127%:%

@@

%:%241=131%:%
%:%244=133%:%
%:%245=134%:%

@@

@@

%:%251=139%:%
%:%252=140%:%

@@

%:%255=142%:%
%:%257=142%:%
%:%261=142%:%
%:%262=142%:%
%:%264=143%:%
%:%265=144%:%

@@

%:%277=148%:%
%:%278=149%:%
%:%287=154%:%
%:%299=156%:%
%:%300=157%:%

@@

%:%305=161%:%
%:%306=161%:%
%:%307=162%:%
%:%309=163%:%
%:%310=164%:%

@@

%:%314=167%:%

@@

%:%317=169%:%
%:%318=170%:%

@@

%:%320=171%:%
%:%322=171%:%
%:%326=171%:%
%:%327=171%:%
%:%329=172%:%
%:%330=173%:%

@@

%:%344=179%:%

@@

%:%347=181%:%

@@

%:%352=185%:%
%:%353=185%:%
%:%355=185%:%
%:%359=185%:%
%:%360=185%:%
%:%362=186%:%
%:%363=187%:%

@@

%:%375=191%:%
%:%376=192%:%

@@

%:%387=197%:%
%:%399=199%:%
%:%400=200%:%

@@

%:%411=209%:%
%:%415=211%:%
%:%416=212%:%

@@

@@

%:%420=215%:%
%:%422=216%:%
%:%423=216%:%
%:%424=217%:%
%:%425=218%:%
%:%426=218%:%
%:%427=219%:%
%:%430=220%:%
%:%434=220%:%
%:%435=220%:%
%:%437=221%:%
%:%438=222%:%
%:%448=224%:%
%:%449=225%:%
%:%450=226%:%
%:%451=227%:%
%:%452=228%:%
%:%453=229%:%
%:%454=230%:%
%:%455=231%:%

@@

%:%466=240%:%
%:%467=241%:%
%:%469=243%:%
%:%470=243%:%
%:%472=244%:%
%:%473=244%:%
%:%474=245%:%
%:%475=246%:%
%:%476=246%:%
%:%477=247%:%
%:%480=248%:%
%:%484=248%:%
%:%485=248%:%
%:%486=249%:%
%:%487=249%:%
%:%488=250%:%
%:%489=250%:%
%:%490=251%:%
%:%491=251%:%
%:%492=251%:%
%:%493=252%:%
%:%503=254%:%
%:%504=255%:%
%:%505=256%:%
%:%506=257%:%
%:%510=259%:%
%:%514=261%:%
%:%515=262%:%
%:%516=263%:%
%:%520=265%:%
%:%521=266%:%
%:%523=268%:%
%:%524=268%:%
%:%537=289%:%
%:%538=290%:%
%:%539=290%:%
%:%541=291%:%
%:%542=292%:%
%:%543=293%:%
%:%544=294%:%
%:%545=295%:%
%:%546=296%:%
%:%547=296%:%
%:%549=297%:%
%:%550=298%:%
%:%551=298%:%
%:%552=299%:%
%:%553=300%:%
%:%554=300%:%
%:%556=301%:%
%:%557=302%:%
%:%560=304%:%
%:%561=305%:%
%:%563=307%:%
%:%564=307%:%
%:%565=308%:%
%:%566=309%:%
%:%567=309%:%
%:%569=309%:%
%:%573=309%:%
%:%574=309%:%
%:%576=310%:%
%:%577=311%:%
%:%578=312%:%
%:%579=313%:%
%:%580=314%:%
%:%581=315%:%
%:%582=316%:%
%:%592=318%:%
%:%593=319%:%
%:%594=320%:%
%:%597=322%:%
%:%598=323%:%
%:%599=324%:%
%:%600=325%:%
%:%601=326%:%
%:%602=327%:%
%:%605=329%:%
%:%607=331%:%
%:%608=331%:%
%:%609=332%:%
%:%612=333%:%
%:%616=333%:%
%:%617=333%:%
%:%619=334%:%
%:%625=334%:%
%:%628=335%:%
%:%629=336%:%
%:%630=336%:%
%:%631=337%:%
%:%632=338%:%
%:%633=339%:%
%:%634=339%:%
%:%636=339%:%
%:%640=339%:%
%:%641=339%:%
%:%643=340%:%
%:%644=341%:%
%:%645=342%:%
%:%646=343%:%
%:%647=344%:%
%:%657=346%:%
%:%658=347%:%
%:%659=348%:%
%:%660=349%:%
%:%661=350%:%
%:%662=351%:%
%:%663=352%:%
%:%664=353%:%
%:%665=354%:%
%:%669=357%:%
%:%670=358%:%
%:%671=359%:%
%:%672=360%:%
%:%673=361%:%
%:%674=362%:%
%:%675=363%:%
%:%676=364%:%
%:%677=365%:%
%:%678=366%:%
%:%679=367%:%

@@

%:%689=370%:%
%:%701=372%:%
%:%702=373%:%
%:%703=374%:%
%:%705=376%:%
%:%706=376%:%
%:%707=377%:%
%:%708=378%:%
%:%709=379%:%
%:%710=379%:%
%:%712=379%:%
%:%716=379%:%
%:%717=379%:%
%:%719=380%:%
%:%720=381%:%
%:%721=382%:%
%:%722=383%:%
%:%732=385%:%
%:%733=386%:%
%:%734=387%:%
%:%738=389%:%
%:%740=391%:%
%:%741=391%:%
%:%742=392%:%
%:%743=393%:%
%:%744=394%:%
%:%745=394%:%
%:%747=394%:%
%:%751=394%:%
%:%752=394%:%
%:%754=395%:%
%:%755=396%:%
%:%756=397%:%
%:%757=398%:%
%:%767=400%:%
%:%768=401%:%
%:%770=403%:%
%:%771=403%:%
%:%772=404%:%
%:%773=405%:%
%:%774=406%:%
%:%775=406%:%
%:%777=406%:%
%:%781=406%:%
%:%782=406%:%
%:%784=407%:%
%:%785=408%:%
%:%786=409%:%
%:%787=410%:%
%:%788=411%:%
%:%798=413%:%
%:%799=414%:%
%:%801=416%:%
%:%802=416%:%
%:%803=417%:%
%:%804=418%:%
%:%807=419%:%
%:%811=419%:%
%:%812=419%:%
%:%813=419%:%
%:%822=421%:%
%:%823=422%:%
%:%824=423%:%
%:%825=424%:%
%:%827=426%:%
%:%828=426%:%
%:%829=427%:%
%:%830=428%:%
%:%833=429%:%
%:%837=429%:%
%:%838=429%:%
%:%839=429%:%
%:%848=431%:%
%:%849=432%:%
%:%851=434%:%
%:%852=434%:%
%:%853=435%:%
%:%854=436%:%
%:%855=437%:%
%:%856=437%:%
%:%858=437%:%
%:%862=437%:%
%:%863=437%:%
%:%865=438%:%
%:%866=439%:%
%:%867=440%:%
%:%868=441%:%
%:%878=443%:%
%:%879=444%:%
%:%880=445%:%
%:%881=446%:%
%:%882=447%:%
%:%883=448%:%
%:%885=450%:%
%:%886=450%:%
%:%887=451%:%
%:%888=452%:%
%:%889=453%:%
%:%890=454%:%
%:%891=454%:%
%:%893=454%:%
%:%897=454%:%
%:%898=454%:%
%:%900=455%:%
%:%901=456%:%
%:%902=457%:%
%:%903=458%:%
%:%904=459%:%
%:%905=460%:%
%:%915=462%:%
%:%916=463%:%
%:%917=464%:%
%:%918=465%:%
%:%919=466%:%
%:%920=467%:%
%:%922=469%:%
%:%923=469%:%
%:%924=470%:%
%:%925=471%:%
%:%928=472%:%
%:%932=472%:%
%:%933=472%:%
%:%935=473%:%
%:%945=475%:%
%:%946=476%:%
%:%947=477%:%
%:%948=478%:%
%:%957=480%:%
%:%969=482%:%
%:%970=483%:%
%:%971=484%:%
%:%972=485%:%
%:%976=487%:%
%:%977=488%:%
%:%979=490%:%
%:%980=490%:%
%:%981=491%:%
%:%982=492%:%
%:%983=492%:%
%:%984=493%:%
%:%987=494%:%
%:%991=494%:%
%:%992=494%:%
%:%993=494%:%
%:%995=495%:%
%:%996=496%:%
%:%1006=498%:%
%:%1007=499%:%
%:%1008=500%:%
%:%1009=501%:%
%:%1010=502%:%
%:%1011=503%:%
%:%1012=504%:%
%:%1013=505%:%
%:%1014=506%:%
%:%1015=507%:%
%:%1016=508%:%

@@

@@

%:%1023=514%:%
%:%1024=515%:%
%:%1025=516%:%
%:%1026=517%:%
%:%1027=517%:%
%:%1029=517%:%
%:%1033=517%:%
%:%1034=517%:%
%:%1036=518%:%
%:%1037=519%:%
%:%1038=520%:%
%:%1039=521%:%
%:%1040=522%:%
%:%1041=523%:%
%:%1051=525%:%
%:%1052=526%:%
%:%1053=527%:%
%:%1054=528%:%
%:%1058=530%:%
%:%1059=531%:%
%:%1060=532%:%
%:%1062=534%:%
%:%1063=534%:%
%:%1064=535%:%
%:%1065=535%:%
%:%1067=536%:%
%:%1068=537%:%
%:%1069=537%:%
%:%1070=538%:%
%:%1071=539%:%
%:%1072=539%:%
%:%1073=540%:%
%:%1076=541%:%
%:%1080=541%:%
%:%1081=541%:%
%:%1083=542%:%
%:%1084=543%:%
%:%1085=544%:%
%:%1095=546%:%
%:%1096=547%:%
%:%1097=548%:%
%:%1098=549%:%
%:%1100=551%:%
%:%1101=551%:%
%:%1102=552%:%
%:%1104=552%:%
%:%1108=552%:%
%:%1109=552%:%
%:%1111=553%:%
%:%1119=553%:%
%:%1120=554%:%
%:%1121=555%:%
%:%1122=555%:%
%:%1123=556%:%
%:%1125=556%:%
%:%1129=556%:%
%:%1130=556%:%
%:%1132=557%:%
%:%1142=559%:%
%:%1143=560%:%
%:%1144=561%:%

>>>>

Once again, the notion of permissibility will be useful here. Recall that an action can either be 
obligated, permissible, or prohibited. A permissible action is acceptable (there is no specific prohibition 
against it), but not required (there is no specific obligation requiring it).%

@@

  Empty assignment\color{black}%
This completes my implementation of Kroy's formalization of the first formulation of the 
categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
that it is both non-trivial and consistent. Now it's time to start testing!%
\isamarkupsubsubsection{Application Tests\label{sec:app_tests_kroy}%
In the following sections, I will use the application and metaethical tests presenting in Sections \ref{sec:app_tests_naive} and \ref{sec:meta_tests_naive}
        to tease out the strengths and weaknesses of Kroy's formalization. While the formalization is considerably
        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means. 
        I will analyze these problems in the context of philosophical scholarship explicating the content 
        of the formula of universal law. The findings in these sections will inform milestones for my
        custom formalization of the categorical imperative. They also serve as an example of how formalized
        and automated ethics can reveal philosophical strengths and weaknesses of an ethical theory.%
\textbf{Murder}%
In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
it is actually wrong.%
\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Let the constant $M$ denote murder. I have defined no features of this constant, except that it is 
of the type term, which can be true or false at a set of worlds. Indeed, this constant as-is has no 
semantic meaning and could be replaced with any symbol, like `Q' or `Going to Target.' This constant 
will begin to take on features of the act of murder when I specify its properties. In the tests below, 
I specify its properties as the antecedents of lemmas. For example, the test below specifies that 
it is possible that murder is prohibited at the current world. This pattern will hold for most constants 
defined in Isabelle—they have no meaning until I program a meaning.%
\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
at all worlds.%
This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
to imply prohibition at $\text{every world}$.

@@

possibly wrong, it is wrong at every world. This implies that this is not a useful example to test any formulation. 
If a lemma is true in the base logic, without any custom axioms added, then it will hold for any set of  
custom axioms. Testing whether or not it holds as we add axioms tells us nothing, since it held in 
the base logic itself. Interesting cases are ones that fail (or are indeterminate) in the base logic, 
but become true as we add axioms.%

@@

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True, $i_2$  := False)
    B = ($\lambda x. \_$)($i_1$  := True, $i_2$  := False)
    w = $i_2$ \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Just as with the naive formalization, Kroy's formalization allows implied contradictions because 
        DDL itself allows implied contradictions and Kroy's 
        formalization doesn't do anything to remedy this.

@@

%:%106=51%:%

@@

%:%109=54%:%

@@

%:%111=55%:%
%:%112=56%:%
%:%113=56%:%
%:%114=57%:%
%:%115=60%:%

@@

%:%121=66%:%
%:%122=67%:%
%:%125=69%:%

@@

%:%132=75%:%

@@

%:%135=78%:%

@@

%:%138=80%:%
%:%139=81%:%
%:%140=81%:%
%:%142=81%:%
%:%146=81%:%
%:%147=81%:%

@@

%:%151=84%:%
%:%152=85%:%

@@

%:%170=95%:%

@@

%:%173=98%:%

@@

%:%176=100%:%
%:%177=101%:%
%:%178=101%:%
%:%180=101%:%
%:%184=101%:%
%:%185=101%:%

@@

%:%189=104%:%
%:%190=105%:%

@@

%:%207=115%:%
%:%208=116%:%
%:%210=119%:%

@@

%:%213=121%:%
%:%214=122%:%
%:%215=122%:%
%:%217=122%:%
%:%221=122%:%
%:%222=122%:%

@@

%:%226=125%:%
%:%227=126%:%

@@

%:%239=130%:%
%:%240=131%:%
%:%243=133%:%

@@

%:%249=138%:%

@@

%:%252=141%:%

@@

%:%255=143%:%
%:%256=144%:%
%:%257=144%:%
%:%259=144%:%
%:%263=144%:%
%:%264=144%:%

@@

%:%268=147%:%
%:%269=148%:%
%:%279=150%:%
%:%280=151%:%
%:%289=156%:%

@@

%:%304=161%:%
%:%305=162%:%
%:%307=163%:%
%:%308=163%:%
%:%309=164%:%

@@

%:%312=166%:%
%:%313=167%:%

@@

%:%318=171%:%

@@

%:%320=172%:%
%:%321=173%:%
%:%322=173%:%
%:%324=173%:%
%:%328=173%:%
%:%329=173%:%

@@

%:%335=178%:%
%:%336=179%:%

@@

%:%348=183%:%

@@

%:%353=187%:%
%:%354=187%:%
%:%355=187%:%
%:%357=187%:%
%:%361=187%:%
%:%362=187%:%

@@

%:%366=190%:%
%:%367=191%:%

@@

%:%379=195%:%
%:%380=196%:%
%:%389=199%:%

@@

%:%408=208%:%
%:%409=209%:%
%:%413=211%:%

@@

%:%418=214%:%

@@

%:%421=217%:%
%:%422=217%:%
%:%424=218%:%
%:%425=219%:%
%:%426=220%:%
%:%427=221%:%
%:%428=222%:%
%:%429=223%:%
%:%430=224%:%
%:%431=224%:%
%:%432=225%:%
%:%433=226%:%
%:%434=226%:%
%:%435=227%:%
%:%438=228%:%
%:%442=228%:%
%:%443=228%:%
%:%445=229%:%
%:%446=230%:%

@@

%:%463=239%:%
%:%464=240%:%
%:%465=241%:%
%:%466=242%:%
%:%467=243%:%
%:%468=244%:%
%:%469=245%:%
%:%470=246%:%
%:%471=247%:%
%:%472=248%:%
%:%473=249%:%
%:%477=251%:%
%:%478=252%:%
%:%480=254%:%
%:%481=254%:%
%:%483=255%:%
%:%484=255%:%
%:%485=256%:%
%:%486=257%:%
%:%487=257%:%
%:%488=258%:%
%:%491=259%:%
%:%495=259%:%
%:%496=259%:%
%:%497=260%:%
%:%498=260%:%
%:%499=261%:%
%:%500=261%:%
%:%501=262%:%
%:%502=262%:%
%:%503=262%:%
%:%504=263%:%
%:%514=265%:%
%:%515=266%:%
%:%516=267%:%
%:%517=268%:%
%:%521=270%:%
%:%525=272%:%
%:%526=273%:%
%:%527=274%:%
%:%531=276%:%
%:%532=277%:%
%:%534=279%:%
%:%535=279%:%
%:%548=300%:%
%:%549=301%:%
%:%550=301%:%
%:%552=302%:%
%:%553=303%:%
%:%554=304%:%
%:%555=305%:%
%:%556=306%:%
%:%557=307%:%
%:%558=307%:%
%:%560=308%:%
%:%561=309%:%
%:%562=309%:%
%:%563=310%:%
%:%564=311%:%
%:%565=311%:%
%:%567=312%:%
%:%568=313%:%
%:%571=315%:%
%:%572=316%:%
%:%574=318%:%
%:%575=318%:%
%:%576=319%:%
%:%577=320%:%
%:%578=320%:%
%:%580=320%:%
%:%584=320%:%
%:%585=320%:%
%:%587=321%:%
%:%588=322%:%
%:%589=323%:%
%:%590=324%:%
%:%591=325%:%
%:%592=326%:%
%:%593=327%:%
%:%603=329%:%
%:%604=330%:%
%:%605=331%:%
%:%608=333%:%
%:%609=334%:%
%:%610=335%:%
%:%611=336%:%
%:%612=337%:%
%:%613=338%:%
%:%616=340%:%
%:%618=342%:%
%:%619=342%:%
%:%620=343%:%
%:%623=344%:%
%:%627=344%:%
%:%628=344%:%
%:%630=345%:%
%:%636=345%:%
%:%639=346%:%
%:%640=347%:%
%:%641=347%:%
%:%642=348%:%
%:%643=349%:%
%:%644=350%:%
%:%645=350%:%
%:%647=350%:%
%:%651=350%:%
%:%652=350%:%
%:%654=351%:%
%:%655=352%:%
%:%656=353%:%
%:%657=354%:%
%:%658=355%:%
%:%668=357%:%
%:%669=358%:%
%:%670=359%:%
%:%671=360%:%
%:%672=361%:%
%:%673=362%:%
%:%674=363%:%
%:%675=364%:%
%:%676=365%:%

@@

%:%681=369%:%
%:%682=370%:%
%:%683=371%:%
%:%684=372%:%
%:%685=373%:%
%:%686=374%:%
%:%687=375%:%
%:%688=376%:%
%:%689=377%:%
%:%690=378%:%
%:%691=379%:%
%:%700=381%:%
%:%712=383%:%
%:%713=384%:%
%:%714=385%:%
%:%716=387%:%
%:%717=387%:%
%:%718=388%:%
%:%719=389%:%
%:%720=390%:%
%:%721=390%:%
%:%723=390%:%
%:%727=390%:%
%:%728=390%:%
%:%730=391%:%
%:%731=392%:%
%:%732=393%:%
%:%733=394%:%
%:%743=396%:%
%:%744=397%:%
%:%745=398%:%
%:%749=400%:%
%:%751=402%:%
%:%752=402%:%
%:%753=403%:%
%:%754=404%:%
%:%755=405%:%
%:%756=405%:%
%:%758=405%:%
%:%762=405%:%
%:%763=405%:%
%:%765=406%:%
%:%766=407%:%
%:%767=408%:%
%:%768=409%:%
%:%778=411%:%
%:%779=412%:%
%:%781=414%:%
%:%782=414%:%
%:%783=415%:%
%:%784=416%:%
%:%785=417%:%
%:%786=417%:%
%:%788=417%:%
%:%792=417%:%
%:%793=417%:%
%:%795=418%:%
%:%796=419%:%
%:%797=420%:%
%:%798=421%:%
%:%799=422%:%
%:%809=424%:%
%:%810=425%:%
%:%812=427%:%
%:%813=427%:%
%:%814=428%:%
%:%815=429%:%
%:%818=430%:%
%:%822=430%:%
%:%823=430%:%
%:%824=430%:%
%:%833=432%:%
%:%834=433%:%
%:%835=434%:%
%:%836=435%:%
%:%838=437%:%
%:%839=437%:%
%:%840=438%:%
%:%841=439%:%
%:%844=440%:%
%:%848=440%:%
%:%849=440%:%
%:%850=440%:%
%:%859=442%:%
%:%860=443%:%
%:%862=445%:%
%:%863=445%:%
%:%864=446%:%
%:%865=447%:%
%:%866=448%:%
%:%867=448%:%
%:%869=448%:%
%:%873=448%:%
%:%874=448%:%
%:%876=449%:%
%:%877=450%:%
%:%878=451%:%
%:%879=452%:%
%:%889=454%:%
%:%890=455%:%
%:%891=456%:%
%:%892=457%:%
%:%893=458%:%
%:%894=459%:%
%:%896=461%:%
%:%897=461%:%
%:%898=462%:%
%:%899=463%:%
%:%900=464%:%
%:%901=465%:%
%:%902=465%:%
%:%904=465%:%
%:%908=465%:%
%:%909=465%:%
%:%911=466%:%
%:%912=467%:%
%:%913=468%:%
%:%914=469%:%
%:%915=470%:%
%:%916=471%:%
%:%926=473%:%
%:%927=474%:%
%:%928=475%:%
%:%929=476%:%
%:%930=477%:%
%:%931=478%:%
%:%933=480%:%
%:%934=480%:%
%:%935=481%:%
%:%936=482%:%
%:%939=483%:%
%:%943=483%:%
%:%944=483%:%
%:%946=484%:%
%:%956=486%:%
%:%957=487%:%
%:%958=488%:%
%:%959=489%:%
%:%968=491%:%
%:%980=493%:%
%:%981=494%:%
%:%982=495%:%
%:%983=496%:%
%:%987=498%:%
%:%988=499%:%
%:%990=501%:%
%:%991=501%:%
%:%992=502%:%
%:%993=503%:%
%:%994=503%:%
%:%995=504%:%
%:%998=505%:%
%:%1002=505%:%
%:%1003=505%:%
%:%1004=505%:%
%:%1006=506%:%
%:%1007=507%:%

@@

%:%1021=513%:%

@@

%:%1023=515%:%
%:%1024=516%:%
%:%1025=517%:%
%:%1026=518%:%
%:%1027=519%:%
%:%1028=520%:%
%:%1029=521%:%
%:%1030=522%:%
%:%1031=523%:%
%:%1033=525%:%
%:%1034=525%:%
%:%1035=526%:%
%:%1036=527%:%
%:%1037=528%:%
%:%1038=528%:%
%:%1040=528%:%
%:%1044=528%:%
%:%1045=528%:%
%:%1047=529%:%
%:%1048=530%:%
%:%1049=531%:%
%:%1050=532%:%
%:%1051=533%:%
%:%1052=534%:%
%:%1062=536%:%
%:%1063=537%:%
%:%1064=538%:%
%:%1065=539%:%
%:%1069=541%:%
%:%1070=542%:%
%:%1071=543%:%
%:%1073=545%:%
%:%1074=545%:%
%:%1075=546%:%
%:%1076=546%:%
%:%1078=547%:%
%:%1079=548%:%
%:%1080=548%:%
%:%1081=549%:%
%:%1082=550%:%
%:%1083=550%:%
%:%1084=551%:%
%:%1087=552%:%
%:%1091=552%:%
%:%1092=552%:%
%:%1094=553%:%
%:%1095=554%:%
%:%1096=555%:%
%:%1106=557%:%
%:%1107=558%:%
%:%1108=559%:%
%:%1109=560%:%
%:%1111=562%:%
%:%1112=562%:%
%:%1113=563%:%
%:%1115=563%:%
%:%1119=563%:%
%:%1120=563%:%
%:%1122=564%:%
%:%1130=564%:%
%:%1131=565%:%
%:%1132=566%:%
%:%1133=566%:%
%:%1134=567%:%
%:%1136=567%:%
%:%1140=567%:%
%:%1141=567%:%
%:%1143=568%:%
%:%1153=570%:%
%:%1154=571%:%
%:%1155=572%:%
